### 2015-07-11 narrative/qos.tex
minor edits.
minor thing on QoS.

\subsubsection{Resource Management}
Careful resource management strategies that can deal with placement and
retrieval of a large number of data chunks spread across the entire storage
hierarchy are key for predictable performance. 
%This connection is particularly important for data retrieval - in large scale
%storage systems, finding a resource to read can be a significant, if not
%dominant, component of overall read latency. 
Locating resources is typical a distributed systems problem. Centralized
solutions suffer scalability challenges due to centralized, serialized system
updates.  POSIX-compliant file systems are good examples of this
strucutre--most updates to files require updates to their centrally maintained
block allocation tables.

An opposite example of this central management strategy are ``pile'' systems,
which, instead of tracking updates, they search for resources upon request.
Pile systems feature efficient writes because clients can write wherever there
is free space with low bookkeeping overhead.  However, unbounded search is
possible, e.g., when it is unclear whether the resource actually exists.
Methods to make searches more efficient without reverting to centralized
bookkeeping usually involves search space partitioning and a method to limit
the search to a small number of partitions.  Frequently this involves a
hash function that is relatively stable against changes to its range, such as
failures or updates to the hardware of the system. Consistent
hashing~\cite{karger:stoc97} is scalable since it can be well-known throughout
a system of any size and only requires minimal movement of data in the presence
of failures or system changes. 
%Consistent hash functions can also have sets of ordered but infinite lists as
%their range (which works well with primary replication)
%~\cite{honicky:ipdps04}, implement declustering (limiting overlap between
%partitions), and support placement policy rules~\cite{weil:sc06}.

@@

\paragraph{Approach:} 
In this proposal, we will investigate the trade-off in terms of predictable
performance between ``filing'' and ``piling'' data.  This trade-off has a
parallel in data management where there are two alternative paths to achieve
knowledge. The analogue to filing is  to ``extract, transform, and load'' (ETL)
data into a warehouse paying an upfront ingest cost to achieve fast querying.
The analogue to piling is to not pay any upfront cost and later querying the
raw data directly by using a data processing platform such as Hadoop.  Recent
work has found that the combination of these two techniques can be optimized to
perform better than any one technique alone~\cite{lefevre:sigmod14a}. We
believe that a similar opportunity exists for combining filing and piling
approaches to achieve performance predictability without sacrificing too much
flexibility. Our additional challenge is incorporating both the storage tiers
and potential data quality metrics.

@@

Consider this example demonstrating this disconnection will hurt system
performance. We launch 4096 processes with each process doing a single file I/O
operation against half of the Spider II file system at ORNL. The file traces
are analyzed to examine the utilization distribution of different components.
Figures (a), (b) and (c) show the resource usage distribution for OSTs, OSSes,
and LNETs, respectively. We observe a significant usage variation
across components of any given type (e.g., OST, OSS or LNET). For example, some
OSTs are used more than 10 times while some others are never used
(corresponding to zero frequency count). Similarly, OSSes and LNETs show
significant usage imbalance under the default placement strategy.
Consequently, imbalanced resource utilization increases the contention at
certain components more than others.

>>>>

\subsubsection{Resource Management}
Careful resource management strategies that can deal with placement and
retrieval of a large number of data chunks spread across the entire storage
hierarchy are key for predictable performance. 
%This connection is particularly important for data retrieval - in large scale
%storage systems, finding a resource to read can be a significant, if not
%dominant, component of overall read latency. 
Locating resources is typical a distributed systems problem. Centralized
solutions suffer scalability challenges due to centralized, serialized system
updates.  POSIX-compliant file systems are good examples of this
strucutre--most updates to files require updates to their centrally maintained
block allocation tables.
An opposite example of this central management strategy are ``pile'' systems,
which, instead of tracking updates, they search for resources upon request.
Pile systems feature efficient writes because clients can write wherever there
is free space with low bookkeeping overhead.  However, unbounded search is
possible, e.g., when it is unclear whether the resource actually exists.
Methods to make searches more efficient without reverting to centralized
bookkeeping usually involves search space partitioning and a method to limit
the search to a small number of partitions.  Frequently this involves a
hash function that is relatively stable against changes to its range, such as
failures or updates to the hardware of the system. Consistent
hashing~\cite{karger:stoc97} is scalable since it can be well-known throughout
a system of any size and only requires minimal movement of data in the presence
of failures or system changes. 
%Consistent hash functions can also have sets of ordered but infinite lists as
%their range (which works well with primary replication)
%~\cite{honicky:ipdps04}, implement declustering (limiting overlap between
%partitions), and support placement policy rules~\cite{weil:sc06}.

@@

\paragraph{Approach:} 
In this proposal, we will investigate the trade-off in terms of predictable
performance between ``filing'' and ``piling'' data.  This trade-off has a
parallel in data management where there are two alternative paths to achieve
knowledge. The analogue to filing is  to ``extract, transform, and load'' (ETL)
data into a warehouse paying an upfront ingest cost to achieve fast querying.
The analogue to piling is to not pay any upfront cost and later querying the
raw data directly by using a data processing platform such as Hadoop.  Recent
work has found that the combination of these two techniques can be optimized to
perform better than any one technique alone~\cite{lefevre:sigmod14a}. We
believe that a similar opportunity exists for combining filing and piling
approaches to achieve performance predictability without sacrificing too much
flexibility. Our additional challenge is incorporating both the storage tiers
and data utility.

@@

Consider this example demonstrating this disconnection will hurt system
performance. We launch 4096 processes with each process doing a single file I/O
operation against half of the Spider II file system at ORNL. The file traces
are analyzed to examine the utilization distribution of different components.
Figures (a), (b) and (c) show the resource usage distribution for OSTs (object storage
target), OSSes (object storage server),
and LNETs (Lustre Networking), respectively. We observe a significant usage variation
across components of any given type (e.g., OST, OSS or LNET). For example, some
OSTs are used more than 10 times while some others are never used
(corresponding to zero frequency count). Similarly, OSSes and LNETs show
significant usage imbalance under the default placement strategy.
Consequently, imbalanced resource utilization increases the contention at
certain components more than others.
